---
title: "R-markdown peergraded asignment"
author: "ROBERT"
date: "11/22/2021"
output: html_document
---
##Reading data from local directory
I will use the function **read.csv** to load the data
```{r}
Activity<-read.csv("D://Self-made//Data science//Project-on-R-markdown//activity.csv")
```
After loading the data, we know hit on the *data mining*
first lets determine the total number of steps taken per day
```{r}
library(tidyverse)
Daily<-Activity%>%
  group_by(date)%>%
  na.omit()%>%
  summarise(DailySteps=sum(steps))
Daily
```
Lets visualize our data with Histogram to check daily steps
```{r}
with(Daily,hist(DailySteps,breaks = 53))
```
Now lets check on the *mean* and the *median*
```{r}
#MEAN
mean(Daily$DailySteps)
#Median
median(Daily$DailySteps)
```
How is the time series of the 5-minute interval looking like, lets see:
```{r}
library(tidyverse)
TimeSeries<-Activity%>%
  group_by(interval)%>%
  na.omit()%>%
  summarise(Average=mean(steps))
with(TimeSeries,plot(interval,Average,type = "l",col="red",main = "5 minute interval"))
#Which is an interval with highest average
TimeSeries$interval[which.max(TimeSeries$Average)]

```
Our dataset seems got a lot of *NAs*, lets see exact number
```{r}
sum(is.na(Activity))
```
I impute the data with **MICE** package to remove NA's
```{r}
library(mice)
DataWithoutNas<-mice::mice(Activity,m=5,method = "pmm",maxit = 50,seed = 500)
```
The Mice package have manipulated the missing values using pmm method, Lets take a look at the manipulated data
```{r}
completedata<-mice::complete(DataWithoutNas,3)
completedata
```
Lets draw an histogram of the completedata 
```{r}
DailyStepSum<-completedata%>%
  group_by(date)%>%
  summarise(DayStep=sum(steps))
with(DailyStepSum,hist(DayStep,breaks = 100,col = "blue"))
```
Lets check the meadian and the mean of the imputed data
```{r}
#MEAN
mean(DailyStepSum$DayStep)
#MEDIAN
median(DailyStepSum$DayStep)
```
## Weekend and weekday
I decided to create a new column, using mutate funtion, clarifying if date is falling on weekend or weekday 
```{r}
library(tidyverse)
completedata$date<-as.Date(completedata$date)
DayClarifiedData<-completedata%>%
  mutate(weekly=ifelse(weekdays(date)=="Saturday"|weekdays(date)=="Sunday","weekend","Weekday"))
DayClarifiedData
```
##Time series for weekend and weekday
```{r}
Weekendays<-DayClarifiedData%>%
  filter(weekly=="weekend")%>%
  group_by(interval)%>%
  na.omit()%>%
  summarise(WeekendMeanStep=mean(steps))
par(mfrow=c(1,2)) 
with(Weekendays,plot(interval,WeekendMeanStep,type="l",col="blue",main = "Weekend 5 minute interval"))
WeekDayDays<-DayClarifiedData%>%
  filter(weekly=="Weekday")%>%
  group_by(interval)%>%
  na.omit()%>%
  summarise(weekdayMeanStep=mean(steps))
with(WeekDayDays,plot(interval,weekdayMeanStep,type = "l",col="red",main = "Weekday 5 minute interval"))
